Supplementary Figures

### 2024-09-03 supplementary_plots.Rmd
reverse the calculation of the relative skill metrics

  # calcaulte the skill relative to climatology (- is bad, + is good)
  mutate(skill_crps = crps_climatology - crps,
         skill_logs = logs_climatology - logs,
         horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) |> 
  # consistent forecast period
  filter(horizon <= 30,
         horizon >= 1, 
         horizon != 15) |> 
  arrange(reference_datetime, site_id, datetime, model_id)

@@

  # calcaulte the skill relative to climatology (- is bad, + is good)
  mutate(skill_crps = crps_persistenceRW - crps,
         skill_logs = logs_persistenceRW - logs,
         horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) |> 
  # consistent forecast period
  filter(horizon <= 30,
         horizon >= 1, 
         horizon != 15) |> 
  arrange(reference_datetime, site_id, datetime, model_id)

@@

  # calcaulte the skill relative to persistenceRW (- is bad, + is good)
  mutate(skill_crps = crps_persistenceRW - crps,
         skill_logs = logs_persistenceRW - logs,
         horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) |> 
  # consistent forecast period
  filter(horizon <= 30,
         horizon >= 1, 
         horizon != 15) |> 
  arrange(reference_datetime, site_id, datetime, model_id)

>>>>

  # calcaulte the skill relative to climatology (- is bad, + is good)
  mutate(skill_crps = crps - crps_climatology,
         skill_logs = logs - logs_climatology,
         horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) |> 
  # consistent forecast period
  filter(horizon <= 30,
         horizon >= 1, 
         horizon != 15) |> 
  arrange(reference_datetime, site_id, datetime, model_id)

@@

  # calcaulte the skill relative to climatology (- is bad, + is good)
  mutate(skill_crps = crps - crps_persistenceRW,
         skill_logs = logs - logs_persistenceRW,
         horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) |> 
  # consistent forecast period
  filter(horizon <= 30,
         horizon >= 1, 
         horizon != 15) |> 
  arrange(reference_datetime, site_id, datetime, model_id)

@@

  # calcaulte the skill relative to persistenceRW (- is bad, + is good)
  mutate(skill_crps = crps - crps_persistenceRW,
         skill_logs = logs - logs_persistenceRW,
         horizon = as.numeric(as_date(datetime) - as_date(reference_datetime))) |> 
  # consistent forecast period
  filter(horizon <= 30,
         horizon >= 1, 
         horizon != 15) |> 
  arrange(reference_datetime, site_id, datetime, model_id)
